Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-05-24 doc/bcspaper/article.tex
Got rid of some of the commented out example code - can restore using VCS if we need it back
latest Maria edits
Changed a couple of sentences in article and tried to cut down the words a bit more

Machine learning to build a classifer of paper type was conducted using random
forest learning \cite{Breiman2001}.  A random forest learning algorithm was
chosen because this is a fast, accurate and widely accepted learning
technology, and because the underlying decision trees can be used to describe
and inspect some of the reasoning behind the predictions made by the final
paper type classifiers.  The feature set consisted of the percentage
composition of the CoreSC labels given to the sentences in each paper i.e. (the
percentage of {\em Background} sentences, the percentage of {\em Hypothesis}
sentences, etc.).  Thus there are 11 features corresponding to the 11 CoreSC
labels.  The random forest learning was conducted using the Orange data mining
library for Python \cite{Curk2005}.  The parameters for the random forest
learner were as the defaults, except with min\_subsets=5 and same\_majority\_pruning=true.  
We used 10-fold cross validation to estimate the precision,
recall and F-measure.

@@

We report the results of the random forest learning as recall, precision and F-measure for each paper type, averaged over a 10-fold cross validation in Table \ref{tab:recallPrecision}. Paper types {\em Research}, {\em Review} and {\em Correspondence} are the most accurate classes, and {\em Viewpoint} is the most difficult paper type to predict.

@@

A confusion matrix for the paper types in given in Table \ref{tab:confusion}. Research papers are usually predicted to belong to the Research class, and are sometimes confused with Case Study. However, Case Study papers are often predicted to be Research or Review. There are fewer Case Study papers for the learning algorithm to train on, and many research papers, so we would expect this outcome. We might also expect that Research and Case Study would share similar paper structures. 
We initially expected the classes Essay, Opinion, Perspective and Viewpoint to be confused, as the four labels all indicate a paper containing an author's personal thoughts on an issue, rather than traditional experiment-driven science. Opinion is confused with Perspective and Viewpoint. Perspective is confused with almost all classes, except Research. Viewpoint is a small class and mostly confused with Opinion and Perspective. From this it would seem that there is a clear grouping of paper types which are very similar, and could better be labelled as a single type: \{Opinion, Perspective, Viewpoint\}. However, Essay appears to be different.

@@

%Use the standard \verb|equation| environment to typeset your equations, e.g.
%
%\begin{equation}
%a \times b = c\;,
%\end{equation}
%
%however, for multiline equations we recommend to use the \verb|eqnarray|
%environment\footnote{In physics texts please activate the class option
%\texttt{vecphys} to depict your vectors in \textbf{\itshape
%boldface-italic} type - as is customary for a wide range of physical
%subjects}.
%\begin{eqnarray}
%a \times b = c \nonumber\\
%\vec{a} \cdot \vec{b}=\vec{c}
%\label{eq:01}
%\end{eqnarray}

%\subsection{Subsection Heading}
%\label{subsec:2}
%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references\index{cross-references} and citations\index{citations} as has already been described in Sect.~\ref{sec:2}.

%\begin{quotation}
%Please do not use quotation marks when quoting texts! Simply use the \verb|quotation| environment -- it will automatically render Springer's preferred layout.
%\end{quotation}

%\subsubsection{Subsubsection Heading}
%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{subsec:2}, see also Fig.~\ref{fig:1}\footnote{If you copy text passages, figures, or tables from other works, you must obtain \textit{permission} from the copyright holder (usually the original publisher). Please enclose the signed permission with the manucript. The sources\index{permission to print} must be acknowledged either in the captions, as footnotes or in a separate section of the book.}

%For typesetting numbered lists we recommend to use the \verb|enumerate| environment -- it will automatically render Springer's preferred layout.

%\begin{enumerate}
%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
%\begin{enumerate}
%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
%\end{enumerate}
%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
%\end{enumerate}

%For unnumbered list we recommend to use the \verb|itemize| environment -- it will automatically render Springer's preferred layout.

%\begin{itemize}
%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development, cf. Table~\ref{tab:1}.}
%\begin{itemize}
%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
%\end{itemize}
%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
%\end{itemize}

%\begin{figure}[t]
%\sidecaption[t]
% Use the relevant command for your figure-insertion program
% to insert the figure file.
% For example, with the option graphics use
%\includegraphics[scale=.65]{figure}
%
% If no graphics program available, insert a blank space i.e. use
%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
%
%\caption{Please write your figure caption here}
%\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page. If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
%\label{fig:2}       % Give a unique label
%\end{figure}

%\runinhead{Run-in Heading Boldface Version} Use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

%\subruninhead{Run-in Heading Italic Version} Use the \LaTeX\ automatism for all your cross-refer\-ences and citations as has already been described in Sect.~\ref{sec:2}\index{paragraph}.

% Use the \index{} command to code your index words
%
% For tables use
%
%\begin{table}
%\caption{Please write your table caption here}
%\label{tab:1}       % Give a unique label
%
% Follow this input for your own table layout
%
%\begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
%\hline\noalign{\smallskip}
%Classes & Subclass & Length & Action Mechanism  \\
%\noalign{\smallskip}\svhline\noalign{\smallskip}
%Translation & mRNA$^a$  & 22 (19--25) & Translation repression, mRNA cleavage\\
%Translation & mRNA cleavage & 21 & mRNA cleavage\\
%Translation & mRNA  & 21--22 & mRNA cleavage\\
%Translation & mRNA  & 24--26 & Histone and DNA Modification\\
%\noalign{\smallskip}\hline\noalign{\smallskip}
%\end{tabular}
%$^a$ Table foot note (with superscript)
%\end{table}
%

%\begin{description}[Type 1]
%\item[Type 1]{That addresses central themes pertainng to migration, health, and disease. In Sect.~\ref{sec:1}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
%\item[Type 2]{That addresses central themes pertainng to migration, health, and disease. In Sect.~\ref{subsec:2}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
%\end{description}

%\begin{svgraybox}
%If you want to emphasize complete paragraphs of texts we recommend to use the newly defined Springer class option \verb|graybox| and the newly defined environment \verb|svgraybox|. This will produce a 15 percent screened box 'behind' your text.

%If you want to emphasize complete paragraphs of texts we recommend to use the newly defined Springer class option and environment \verb|svgraybox|. This will produce a 15 percent screened box 'behind' your text.
%\end{svgraybox}

%\begin{theorem}
%Theorem text goes here.
%\end{theorem}
%
% or
%
%\begin{definition}
%Definition text goes here.
%\end{definition}

%\begin{proof}
%\smartqed
%Proof text goes here.
%\qed
%\end{proof}

%\paragraph{Paragraph Heading} %
%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

%Note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
%
% For built-in environments use
%
%\begin{theorem}
%Theorem text goes here.
%\end{theorem}
%
%\begin{definition}
%Definition text goes here.
%\end{definition}
%
%\begin{proof}
%\smartqed
%Proof text goes here.
%\qed
%\end{proof}
%

%
%\section*{Appendix}
%\addcontentsline{toc}{section}{Appendix}
%%
%%
%When placed at the end of a chapter or contribution (as opposed to at the end of the book), the numbering of tables, figures, and equations in the appendix section continues on from that in the main text. Hence please \textit{do not} use the \verb|appendix| command when writing an appendix at the end of your chapter or contribution. If there is only one the appendix is designated ``Appendix'', or ``Appendix 1'', or ``Appendix 2'', etc. if there is more than one.

%\begin{equation}
%a \times b = c
%\end{equation}

>>>>

Random forest learning\cite{Breiman2001} was chosen for the construction of the
paper type classifier. This is because random forests are a fast, accurate and
widely accepted learning technology, and the underlying decision trees can be
inspected to understand some of the reasoning behind the predictions made by
the final paper type classifiers. The feature set consisted of the percentage
composition of each of the 11 respective CoreSC labels assigned to the
sentences in each paper i.e. (the percentage of {\em Background} sentences, the
percentage of {\em Hypothesis} sentences, etc.). The random forest learning was
conducted using the Orange data mining library for Python \cite{Curk2005}.  The
parameters for the random forest learner were as the defaults, except with
min\_subsets=5 and same\_majority\_pruning=true.  We used 10-fold cross
validation to estimate the precision, recall and F-measure.

@@

The results of the random forest learning as recall, precision and F-measure
for each paper type, averaged over a 10-fold cross validation are shown in Table
\ref{tab:recallPrecision}. Paper types {\em Research}, {\em Review} and {\em
Correspondence} are the most accurate classes, and {\em Viewpoint} is the most
difficult paper type to predict.

@@

A confusion matrix for the paper types in given in Table \ref{tab:confusion}.
Research papers are classified correctly most frequently, but are sometimes
confused with Case Study. However, Case Study papers are often predicted to be
Research or Review. There are fewer Case Study papers for the learning
algorithm to train on, and many research papers, so we would expect this
outcome. We might also expect that Research and Case Study would share similar
paper structures.  We initially expected the classes Essay, Opinion,
Perspective and Viewpoint to be confused, as the four labels all indicate a
paper containing an author's personal thoughts on an issue, rather than
traditional experiment-driven science. Opinion is confused with Perspective and
Viewpoint. Perspective is confused with almost all classes, except Research.
Viewpoint is a small class and mostly confused with Opinion and Perspective.
From this it would seem that there is a clear grouping of paper types which are
very similar, and could better be labelled as a single type: \{Opinion,
Perspective, Viewpoint\}. However, Essay appears to be different.

@@
